An open-source integrated framework for the automation of citation collection and screening in systematic reviews.

### 2022-02-03 Manuscript/Manuscript.Rmd
uodate abstract

---
title: An open-source integrated framework for the automation of citation collection and screening in systematic reviews. 
authors:
  - name: Angelo D'Ambrosio
    department: Institute for Infection Prevention and Hospital Hygiene
    affiliation: Freiburg University Hospital
    location: Freiburg, Germany
    email: angelo.d.ambrosio@uniklinik-freiburg.de; a.dambrosioMD@gmail.com
  - name: Hajo Grundmann
    department: Institute for Infection Prevention and Hospital Hygiene
    affiliation: Freiburg University Hospital
    location: Freiburg, Germany
    email: hajo.grundmann@uniklinik-freiburg.de
  - name: Tjibbe Donker
    department: Institute for Infection Prevention and Hospital Hygiene
    affiliation: Freiburg University Hospital
    location: Freiburg, Germany
    email: tjibbe.donker@uniklinik-freiburg.de
abstract: |
  The exponential growth in scientific production makes its summarisation through secondary literature exceedingly demanding in terms of time and human resources.
  We introduce a new open-source framework that significantly increases efficiency during the citation collection and screening phases of systematic reviews.\
  The framework introduces three main tools:
  1) an automatic citation search engine and manager that allows collecting records from multiple citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax;
  2) a citation screening tool based on Bayesian active machine learning and natural language processing, which requires users feedback only on uncertain classifications to increase predictive accuracy iteratively;
  3) a semi-automatic data-driven query generator to create new search queries from existing reviewed citation data sets.\
  The framework was applied on an example topic performing citation collection and screening.
  We estimated median posterior Sensitivity and Efficiency [90% Credible Intervals] using Bayesian simulation to predict the distribution of possibly missed relevant matches in the unreviewed records.\
  17755 unique records were collected through the framework citation manager;
  101 over 766 records were found to be relevant after manual evaluation, while the rest were excluded by the automatic classification;
  the expected Efficiency was 95.7% [95.3%, 95.7%] for a Sensitivity of 100% [93.5%, 100%].
  A new search query was generated from the labelled dataset, and 82579 more records were collected. Only 567 records required human review after the automatic screening, and six additional positive matches were found.
  Including the additional records, the overall expected Sensitivity dropped to 97.3% [73.8%, 100%] while the Efficiency raised to 98.6% [98.2%, 98.7%].\
  The framework can significantly reduce human resources requirements for systematic reviews by simplifying citation collection and screening while demonstrating exceptional sensitivity even on large data sets.
keywords:
  - Systematic review automation
  - Citation management
  - Online data collection
  - Active machine learning
  - Natural language processing
  - Bayesian modeling
bibliography: references.bib
lang: en-GB
output: 
  rticles::arxiv_article:
    number_sections: no
    keep_tex: true
    includes:
      in_header: header.tex
---

>>>>

---
title: An open-source integrated framework for the automation of citation collection and screening in systematic reviews. 
authors:
  - name: Angelo D'Ambrosio
    department: Institute for Infection Prevention and Hospital Hygiene
    affiliation: Freiburg University Hospital
    location: Freiburg, Germany
    email: angelo.d.ambrosio@uniklinik-freiburg.de; a.dambrosioMD@gmail.com
  - name: Hajo Grundmann
    department: Institute for Infection Prevention and Hospital Hygiene
    affiliation: Freiburg University Hospital
    location: Freiburg, Germany
    email: hajo.grundmann@uniklinik-freiburg.de
  - name: Tjibbe Donker
    department: Institute for Infection Prevention and Hospital Hygiene
    affiliation: Freiburg University Hospital
    location: Freiburg, Germany
    email: tjibbe.donker@uniklinik-freiburg.de
abstract: |
  The exponential and prolific growth of published original scientific contributions makes secondary literature abridgements increasingly demanding.
  We introduce a new open-source framework for systematic reviews that significantly reduces time and human resource allocation for text identification, collection, and screening of scientific literature.\
  The framework introduces three main tools:
  1) an automatic citation search engine and manager that allows collecting records from multiple citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified query syntax;
  2) a citation screening tool based on Bayesian active machine learning and natural language processing, which requires users feedback only on uncertain classifications to iteratively increase predictive accuracy;
  3) a semi-automatic data-driven query generator to create new search queries from existing reviewed citation data sets.\
  The framework was tested on an example topic to perform citation collection and screening of related scientific production.
  To evaluate the performance of the active machine learning classifier,
  we estimated the median posterior Sensitivity and Efficiency [90% Credible Intervals] using Bayesian simulation to predict the distribution of potentially relevant matches among the records not manually reviewed.\
  17755 unique records were collected through the framework citation manager;
  101 over 766 records were found to be relevant after manual evaluation,
  while the rest were excluded by automatic classification;
  the expected Efficiency was 95.7% [95.3%, 95.7%] with a Sensitivity of 100% [93.5%, 100%].\
  An additional search query generated from the labelled dataset,
  retrieved 82579 additional records of which only 567 records required human review and six additional positive matches were retrieved.
  Including the additional records, the overall expected Sensitivity decreased to 97.3% [73.8%, 100%] while the Efficiency achieved was 98.6% [98.2%, 98.7%].\
  For large studies, the developed framework significantly reduces workload, human effort and error,
  simplifying citation collection and screening with exceptional sensitivity,
  hence improving the standardization and repeatability of systematic reviews.
keywords:
  - Systematic review automation
  - Citation management
  - Online data collection
  - Active machine learning
  - Natural language processing
  - Bayesian modeling
bibliography: references.bib
lang: en-GB
output: 
  rticles::arxiv_article:
    number_sections: no
    keep_tex: true
    includes:
      in_header: header.tex
---

### 2022-02-03 Manuscript/Manuscript.tex
uodate abstract

\begin{abstract}
The exponential growth in scientific production makes its summarisation
through secondary literature exceedingly demanding in terms of time and
human resources. We introduce a new open-source framework that
significantly increases efficiency during the citation collection and
screening phases of systematic reviews.\\
The framework introduces three main tools: 1) an automatic citation
search engine and manager that allows collecting records from multiple
citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified
query syntax; 2) a citation screening tool based on Bayesian active
machine learning and natural language processing, which requires users
feedback only on uncertain classifications to increase predictive
accuracy iteratively; 3) a semi-automatic data-driven query generator to
create new search queries from existing reviewed citation data sets.\\
The framework was applied on an example topic performing citation
collection and screening. We estimated median posterior Sensitivity and
Efficiency {[}90\% Credible Intervals{]} using Bayesian simulation to
predict the distribution of possibly missed relevant matches in the
unreviewed records.\\
17755 unique records were collected through the framework citation
manager; 101 over 766 records were found to be relevant after manual
evaluation, while the rest were excluded by the automatic
classification; the expected Efficiency was 95.7\% {[}95.3\%, 95.7\%{]}
for a Sensitivity of 100\% {[}93.5\%, 100\%{]}. A new search query was
generated from the labelled dataset, and 82579 more records were
collected. Only 567 records required human review after the automatic
screening, and six additional positive matches were found. Including the
additional records, the overall expected Sensitivity dropped to 97.3\%
{[}73.8\%, 100\%{]} while the Efficiency raised to 98.6\% {[}98.2\%,
98.7\%{]}.\\
The framework can significantly reduce human resources requirements for
systematic reviews by simplifying citation collection and screening
while demonstrating exceptional sensitivity even on large data sets.
\end{abstract}

>>>>

\begin{abstract}
The exponential and prolific growth of published original scientific
contributions makes secondary literature abridgements increasingly
demanding. We introduce a new open-source framework for systematic
reviews that significantly reduces time and human resource allocation
for text identification, collection, and screening of scientific
literature.\\
The framework introduces three main tools: 1) an automatic citation
search engine and manager that allows collecting records from multiple
citation databases (Pubmed, WOS, SCOPUS, EMBASE, IEEE) with a unified
query syntax; 2) a citation screening tool based on Bayesian active
machine learning and natural language processing, which requires users
feedback only on uncertain classifications to iteratively increase
predictive accuracy; 3) a semi-automatic data-driven query generator to
create new search queries from existing reviewed citation data sets.\\
The framework was tested on an example topic to perform citation
collection and screening of related scientific production. To evaluate
the performance of the active machine learning classifier, we estimated
the median posterior Sensitivity and Efficiency {[}90\% Credible
Intervals{]} using Bayesian simulation to predict the distribution of
potentially relevant matches among the records not manually reviewed.\\
17755 unique records were collected through the framework citation
manager; 101 over 766 records were found to be relevant after manual
evaluation, while the rest were excluded by automatic classification;
the expected Efficiency was 95.7\% {[}95.3\%, 95.7\%{]} with a
Sensitivity of 100\% {[}93.5\%, 100\%{]}.\\
An additional search query generated from the labelled dataset,
retrieved 82579 additional records of which only 567 records required
human review and six additional positive matches were retrieved.
Including the additional records, the overall expected Sensitivity
decreased to 97.3\% {[}73.8\%, 100\%{]} while the Efficiency achieved
was 98.6\% {[}98.2\%, 98.7\%{]}.\\
For large studies, the developed framework significantly reduces
workload, human effort and error, simplifying citation collection and
screening with exceptional sensitivity, hence improving the
standardization and repeatability of systematic reviews.
\end{abstract}
